\documentclass[main.tex]{subfiles}
\begin{document}
\chapter{Duality}\label{chap:duality}
\marginnote[-6\baselineskip]{
	\etocsettocstyle{}{}
	\etocsettocdepth{1}
	\localtableofcontents
}
The concept of duality is ubiquitous throughout mathematics. It can relate two perspectives of the same object as for "dual@@VECT" "vector spaces", two complementary optimization problems such as a maximization and a minimization linear program and even two seemingly unrelated subjects like topology and logic (\href{https://en.wikipedia.org/wiki/Stone_duality}{Stone duality}). While this vague principle of duality is behind many groundbreaking results, the duality in question here is categorical "duality@@CAT" and it is a bit more precise.%TODO: ref.

Informally, there is nothing more to say than ``Take all the diagrams in a definition/theorem, reverse the arrows and reap the benefits of the "dual@@CAT" concept/result.''\footnote{In my opinion, this is already a very good reason to learn category theory because we can basically get twice as much math as before by framing things with a categorical language.} The more formal version will follow after we first exhibit the principle in action.

Recall that, intuitively, a "functor" is a structure-preserving transformation between "categories". A simple example we have seen is "functors" between "posets" that are "order-preserving" functions. However, as a consequence, one might conclude that "order-reversing" functions impair the structure of a "poset", which feels arbitrary. The same happens between "deloopings" of "groups" because "anti-homomorphisms"\footnote{\AP An ""anti-homomorphism"" $f: G \rightarrow H$ is a function satisfying $f(gg') = f(g')f(g)$ and $f(1_G) = f(1_H)$.} do not arise as "functors" between such "categories".

For a more concrete situation, recall the "powerset functor" $\mPcov$ described in Example \ref{exmp:functors}.\ref{exmp:powersetcov}. It assigns to any set $X$ the "powerset" $\mPcov X$, and to any function $f: X \rightarrow Y$ the image function $\mPcov(f): \mPcov X \rightarrow \mPcov Y$. There is another important function associated to $f$ between "powersets": the inverse image $f^{-1}$ that assigns to $S \subset Y$ the set of points in $X$ whose images are in $S$. Unfortunately, $f^{-1}$ goes in the ``wrong'' direction $\mP Y \rightarrow \mP X$.

This is quite unsatisfactory because the assignment $f \mapsto f^{-1}$ is well-behaved, e.g. we have $\id_X^{-1} = \id_{\mP X}$ for any set $X$ and, for any functions $f: X \rightarrow Y$ and $g: Y \rightarrow X$, $(f \circ g)^{-1} = g^{-1} \circ f^{-1}$. This second equation looks just like the second condition on "functors" reversed. In words, taking the inverse image \textit{preserves} "composition" but in reverse.

It seems arbitrary to distinguish between both options. There are two options to remedy this discrepancy between intuition and formalism; both have "duality@@CAT" as an underlying principle. In this chapter, we will describe the two options, dismiss one of them, and showcase the strength of "duality@@CAT" while exploring more basic category theory.
\section{Contravariant Functors}
By modifying Definition \ref{defn:func} to require that $F(f)$ goes in the opposite direction, we obtain a "contravariant functor". \AP Incidentally, what we defined as a "functor" before is also called a ""covariant"" "functor".
\begin{defn}[Contravariant functor]\label{defn:contrafunc}
	\AP Let $\mathbf{C}$ and $\mathbf{D}$ be "categories", a ""contravariant functor"" $F: \mathbf{C} \rightsquigarrow \mathbf{D}$ is a pair of maps $F_0:\obj{\mathbf{C}} \rightarrow \obj{\mathbf{D}}$ and $F_1:\mor{\mathbf{C}} \rightarrow \mor{\mathbf{D}}$ making diagrams \eqref{diag:contrafunc1}, \eqref{diag:contrafunc2} and \eqref{diag:contrafunc3} commute.\footnote{Where $F_2'$ is now induced by the definition of $F_1$ with $(f,g) \mapsto (F_1(g), F_1(f))$.}
	\begin{equation}\label{diag:contrafunc1}
	\begin{tikzcd}
	\obj{\mathbf{C}} \arrow[d, "F_0"'] & \mor{\mathbf{C}} \arrow[d, "F_1"] \arrow[l, "\source"'] \arrow[r, "\target"] & \obj{\mathbf{C}} \arrow[d, "F_0"] \\
	\obj{\mathbf{D}} & \mor{\mathbf{D}} \arrow[l, "\target"] \arrow[r, "\source"'] & \obj{\mathbf{D}}
	\end{tikzcd}
	\end{equation}
	\begin{minipage}{0.49\textwidth}
		\begin{equation}\label{diag:contrafunc2}
		\begin{tikzcd}
		\mathbf{C}_2 \arrow[d, "\circ_{\mathbf{C}}"'] \arrow[r, "F_2'"] & \mortwo{\mathbf{D}} \arrow[d, "\circ_{\mathbf{D}}"] \\
		\mor{\mathbf{C}} \arrow[r, "F_1"'] & \mor{\mathbf{D}}
		\end{tikzcd}
		\end{equation}
	\end{minipage}
	\begin{minipage}{0.49\textwidth}
		\begin{equation}\label{diag:contrafunc3}
		\begin{tikzcd}
		\obj{\mathbf{C}} \arrow[d, "\idu_{\mathbf{C}}"'] \arrow[r, "F_0"] & \obj{\mathbf{D}} \arrow[d, "\idu_{\mathbf{D}}"] \\
		\mor{\mathbf{C}} \arrow[r, "F_1"'] & \mor{\mathbf{D}}
		\end{tikzcd}
		\end{equation}
	\end{minipage}\\
	In words, $F$ must satisfy the following properties.
	\begin{enumerate}[i.]
		\item For any $A, B \in \obj{\mathbf{C}}$, if $f \in \Hom_{\mathbf{C}}(A,B)$ then $F(f) \in \Hom_{\mathbf{D}}(F(B), F(A))$.
		\item If $f,g \in \mor{\mathbf{C}}$ are "composable", then $F(f\circ g) = F(g) \circ F(f)$.
		\item If $A \in \obj{\mathbf{C}}$, then $\idu_{\mathbf{D}}(F(A)) = F(\idu_{\mathbf{C}}(A))$.
	\end{enumerate}
\end{defn}
\begin{exmps}
	Just like their "covariant" counterparts, "contravariant functors" are quite numerous. Here are a couple of simple ones.
	\begin{enumerate}
		\item "Contravariant" "functors" $F: (X, \leq) \rightsquigarrow (Y, \sqsubseteq)$ correspond to "order-reversing" functions between the posets $X$ and $Y$ and contravariant functors $F: \deloop{G}\rightsquigarrow \deloop{H}$ correspond to "anti-homomorphisms" between the "groups" $G$ and $H$.
		\itemAP The ""contravariant powerset functor"" $\mPcontr{\placeholder}: \catSet \rightsquigarrow \catSet$ sends a set $X$ to its "powerset" $\mPcontr{X}$,\footnote{We use a different notation for the "powerset" to emphasize the difference between $\mPcov$ and $\mPcontr{\placeholder}$.} and a function $f: X\rightarrow Y$ to the preimage map $\mPcontr{f}:\mPcontr{Y}\rightarrow \mPcontr{X}$, the latter sends a subset $S\subseteq Y$ to \[\mPcontr{f}(S) = f^{-1}(S) := \{x \in X \mid f(x) \in S\} \subseteq X.\]
	\end{enumerate}
\end{exmps}
Next, there is a couple of "functors" that are key to understand the philosophy put forward by category theory.\footnote{We will talk more about it when covering the "Yoneda lemma" in Chapter \ref{chap:Yoneda}.}
\begin{exmp}[Hom functors]\label{exmp:homfunctor}
	\AP Let $\mathbf{C}$ be a "locally small" "category" and $A \in \obj{\mathbf{C}}$ one of its "objects".\footnote{We need "local smallness" so that each $\Hom_{\mathbf{C}}(A,B)$ is a set and the "functors" land in $\catSet$.} We define the "covariant" and "contravariant" ""Hom functors"" from $\mathbf{C}$ to $\catSet$.
	\begin{enumerate}
		\item The "covariant" "Hom functor" $\Hom_{\mathbf{C}}(A,\placeholder): \mathbf{C} \rightsquigarrow \catSet$ sends an "object" $B\in \obj{\mathbf{C}}$ to the "hom-set" $\Hom_{\mathbf{C}}(A,B)$ and a "morphism" $f:B\rightarrow B'$ to the function \[\Hom_{\mathbf{C}}(A,f): \Hom_{\mathbf{C}}(A,B) \rightarrow \Hom_{\mathbf{C}}(A,B') = g \mapsto f\circ g.\]
		\AP This function is called ""post-composition by"" $f$ and is denoted $f \circ (\placeholder)$.\footnote{Some authors denote $f \circ (\placeholder)$ as $f^*$, we prefer to keep this notation for later (see "pullbacks").} Let us show $\Hom_{\mathbf{C}}(A, \placeholder)$ is a "covariant" "functor".
		\begin{enumerate}[i.]
			\item For any $f \in \mor{\mathbf{C}}$, it is clear from the definition that \[\Hom_{\mathbf{C}}(A,\source(f)) = \source(f \circ (\placeholder)) \text{ and } \Hom_{\mathbf{C}}(A,\target(f)) = \target(f \circ (\placeholder)).\]
			\item For any $(f_1,f_2) \in \mathbf{C}_2$, we claim that \[\Hom_{\mathbf{C}}(A,f_1\circ f_2) = \Hom_{\mathbf{C}}(A,f_1)\circ \Hom_{\mathbf{C}}(A,f_2).\] In the L.H.S., an element $g \in \Hom_{\mathbf{C}}(A,\source(f_1\circ f_2))$ is mapped to $(f_1 \circ f_2) \circ g$ and in the R.H.S., an element $g \in \Hom_{\mathbf{C}}(A,\source(f_2))$ is mapped to $f_1\circ (f_2 \circ g)$. Since $\source(f_1 \circ f_2) = \source(f_2)$ and "composition" is "associative", we conclude that the two maps are the same.
			\item For any $B \in \obj{\mathbf{C}}$, the "post-composition" by $\idu_{\mathbf{C}}(B)$ is defined to be the identity,\footnote{Namely, for any $f: A \rightarrow B$, $\idu_{\mathbf{C}}(B) \circ f = f$.} hence \eqref{diag:func3} also commutes.
		\end{enumerate}
		\item The "contravariant" "Hom functor" $\Hom_{\mathbf{C}}(\placeholder,A): \mathbf{C} \rightsquigarrow \catSet$ sends an "object" $B\in \obj{\mathbf{C}}$ to the "hom-set" $\Hom_{\mathbf{C}}(B,A)$ and a "morphism" $f:B\rightarrow B'$ to the function \[\Hom_{\mathbf{C}}(f,A): \Hom_{\mathbf{C}}(B',A) \rightarrow \Hom_{\mathbf{C}}(B,A) = g \mapsto g\circ f.\]
		\AP This function is called ""pre-composition by"" $f$ and is denoted $(\placeholder) \circ f$.\footnote{Some authors denote $(\placeholder) \circ f$ as $f_*$, we prefer to keep this notation for later (see "pushouts").} Let us show $\Hom_{\mathbf{C}}(\placeholder,A)$ is a "contravariant functor".
		\begin{enumerate}[i.]
			\item For any $f \in \mor{\mathbf{C}}$, it is clear from the definition that \[\Hom_{\mathbf{C}}(\source(f),A) = \target((\placeholder) \circ f))\text{ and } \Hom_{\mathbf{C}}(\target(f),A) = \source((\placeholder) \circ f).\]
			\item For any $(f_1,f_2) \in \mathbf{C}_2$, we claim that \[\Hom_{\mathbf{C}}(f_1\circ f_2,A) = \Hom_{\mathbf{C}}(f_2,A)\circ \Hom_{\mathbf{C}}(f_1,A).\] In the L.H.S., an element $g \in \Hom_{\mathbf{C}}(\target(f_1\circ f_2),A)$ is mapped to $g\circ (f_1 \circ f_2)$ and in the R.H.S., an element $g \in \Hom_{\mathbf{C}}(\target(f_1),A)$ is mapped to $(g\circ f_1) \circ f_2$. Since $\target(f_1 \circ f_2) = \target(f_1)$ and "composition" is "associative", we conclude that the two maps are the same.
			\item For any $B \in \obj{\mathbf{C}}$, "pre-composition" by $\idu_{\mathbf{C}}(B)$ is defined to be the identity,\footnote{Namely, for any $f: B \rightarrow A$, $f \circ \idu_{\mathbf{C}}(B) = f$.} hence \eqref{diag:contrafunc3} also commutes.
		\end{enumerate}
	\end{enumerate}
\end{exmp}
It can take a bit of time to get comfortable with "Hom functors". For now, we only give one example of a "contravariant" "Hom functor", but we will take more time to play with them later in the book.
\begin{exmp}["Dual vector space"]
	In the "category" $\catVect{k}$, there is a special "object" $k$,\footnote{We know it is special because we know some linear algebra, but $k$ also has some interesting categorical properties (see Exercise \ref{exer:duality:zeroinvect}).} let us see what the "contravariant functor" $\Hom_{\catVect{k}}(\placeholder, k)$ does. It assigns to any "vector space" $V$ the set of "linear maps" $V \rightarrow k$, that is, the carrier set of the "dual space" $\dual{V}$. It assigns to "linear maps" $T: V \rightarrow W$, the function \[\Hom_{\catVect{k}}(W,k) \rightarrow \Hom_{\catVect{k}}(V,k) = \phi \mapsto \phi \circ T.\]
	We know that $\Hom_{\catVect{k}}(V,k) = \dual{V}$ can be seen as a "vector space" and it is easy to check that "pre-composition" by $T$ is a "linear map" $\dual{W} \rightarrow \dual{V}$. Therefore, we find that the assignment $V \mapsto \dual{V} = \Hom_{\catVect{k}}(\placeholder,k)$ is a "contravariant functor" $\catVect{k} \rightsquigarrow \catVect{k}$.
\end{exmp}
We will not dwell too long on "contravariant functors" as we will see right away how they can be avoided, but first, let us give a reason why we want to avoid them.
\begin{exer}\label{exer:duality:composecontra}\marginnote{\hyperref[soln:duality:composecontra]{See solution.}}
	Let $F: \mathbf{C} \rightsquigarrow \mathbf{D}$, $G: \mathbf{D} \rightsquigarrow \mathbf{E}$ be "contravariant functors", and $G \circ F:\mathbf{C} \rightsquigarrow \mathbf{E}$ be their "composition@@FUNC" defined by $G_0 \circ F_0$ on "objects" and $G_1 \circ F_1$ on "morphisms". Show that $G \circ F$ is a \emph{"covariant"} "functor".\footnote{We conclude that we cannot straightforwardly compose "contravariant functors". This alone makes the following alternative more desirable because we want "functors" to be "morphisms" in a "category", hence they must be composable.} Using diagrams will be easier.
\end{exer}
\section{Opposite Category}
Another way to deal with "order-reversing" maps $(X, \leq) \rightarrow (Y, \subseteq)$ is to consider the reverse order on $X$ and a "covariant" "functor" $(X, \geq) \rightsquigarrow (Y, \subseteq)$. This also works for "anti-homomorphisms" by constructing the opposite "group" $\op{G}$ in which the operation is reversed, namely $g\op{\cdot} h = hg$. The "opposite" "category" is a generalization of these constructions.

\begin{defn}[Opposite category]
	\AP Let $\mathbf{C}$ be a "category", we denote the ""opposite"" "category" with $\op{\mathbf{C}}$ and define it by\footnote{Intuitively, we reverse the direction of all "morphisms" in $\mathbf{C}$ and reverse the order of "composition" as well.}
	\[ \obj{\op{\mathbf{C}}} = \obj{\mathbf{C}},\ \mor{\op{\mathbf{C}}} = \mor{\mathbf{C}},\ \op{\source} = \target,\ \op{\target} = \source,\ \idu_{\op{\mathbf{C}}} = \idu_{\mathbf{C}}\]
	with the "composition" defined by $\op{f}\op{\circ}\op{g} = \op{(g\circ f)}$.\footnote{Note that the $\op{\placeholder}$ notation here is just used to distinguish elements in $\mathbf{C}$ and $\op{\mathbf{C}}$ but the "collection" of "objects" and "morphisms" are the same.} This naturally leads to the following "contravariant functor" $\op{(\placeholder)}_{\mathbf{C}}: \mathbf{C} \rightsquigarrow \op{\mathbf{C}}$ which sends an "object" $A$ to $\op{A}$ and a "morphism" $f$ to $\op{f}$. \AP It is called the ""opposite functor"".
\end{defn}
With this definition, one can see "contravariant functors" as "covariant" "functors". Formally, let $F:\mathbf{C}\rightsquigarrow \mathbf{D}$ be a "contravariant functor", we can view $F$ as "covariant" "functor" from $\op{\mathbf{C}}$ to $\mathbf{D}$ or from $\mathbf{C}$ to $\op{\mathbf{D}}$ via the compositions $F\circ \op{(\placeholder)}_{\op{\mathbf{C}}}$ and $\op{(\placeholder)}_{D}\circ F$ respectively.\footnote{Recall from Exercise \ref{exer:duality:composecontra} that these "compositions" are "covariant".}

In the rest of this book, we choose to work with "covariant" "functors" of type $\op{\mathbf{C}} \rightsquigarrow \mathbf{D}$ instead of "contravariant functors" $\mathbf{C} \rightsquigarrow \mathbf{D}$,\footnote{We still had to learn about "contravariant functors" because you might encounter them in the wild.} and "functors" will be "covariant" by default.
\begin{exmps}
	\begin{enumerate}
		\item As hinted at before, the "category" corresponding to $(X, \geq)$ is the "opposite" "category" of $(X, \leq)$ and $\op{(\deloop{G})}$ is the "category" corresponding to the "opposite" "group" of $G$, i.e.: $\op{(\deloop{G})}= \deloop{(\op{G})}$.
	% While there are other interesting examples, the "opposite" construction is usually used implicitly to avoid dealing with "contravariant" functors or to avoid proving the "dual@@CAT" of an already proven result.

	\item We have seen that "functors" $\deloop{G} \rightsquigarrow \catSet$ correspond to "left actions" of a "group" $G$. You can check that "functors" $\op{\deloop{G}} \rightsquigarrow \catSet$ correspond to "right actions" of $G$.
	
	\item The two $\Hom$ "functors" defined in Example \ref{exmp:homfunctor} are now written 
	\[\Hom_{\mathbf{C}}(A, \placeholder): \mathbf{C} \rightsquigarrow \catSet \text{ and } \Hom_{\mathbf{C}}(\placeholder,A) : \op{\mathbf{C}} \rightsquigarrow \catSet.\]
	By Exercise \ref{exer:catfunc:funccomponent}, they can be combined into a "functor" \[\Hom_{\mathbf{C}}(\placeholder,\placeholder): \op{\mathbf{C}}\cattimes \mathbf{C} \rightsquigarrow \catSet\] acting on "objects" as $(A,B) \mapsto \Hom_{\mathbf{C}}(A,B)$ and on "morphisms" as $(f,g) \mapsto (g \circ \placeholder \circ f)$. The condition in Exercise \ref{exer:catfunc:funccomponent} is satisfied because\footnote{Looking at where the "source" and "target" functions are applied, these equalities do not match exactly what is in Exercise \ref{exer:catfunc:funccomponent} since $\Hom_{\mathbf{C}}(\placeholder,\placeholder)$ is "contravariant" in the first component.}
	\begin{align*}
		\Hom_{\mathbf{C}}(f,g) &= g \circ \placeholder \circ f\\
		 &= \id_{\target(g)} \circ (g \circ \placeholder \circ \id_{\target(f)}) \circ f = \Hom_{\mathbf{C}}(f,\id_{\target(g)}) \circ \Hom_{\mathbf{C}}(\id_{\target(f)},g)\\
		 &= g \circ (\id_{\source(g)} \circ \placeholder \circ f) \circ \id_{\source(f)} = \Hom_{\mathbf{C}}(\id_{\source(f)},g) \circ \Hom_{\mathbf{C}}(f,\id_{\source(g)}).
	\end{align*}
	This will be called the $\Hom$ ""bifunctor@hombif"".
\end{enumerate}
\end{exmps}
\begin{exer}\label{exer:duality:oppositefunc}\marginnote{\hyperref[soln:duality:oppositefunc]{See solution.}}
	Let $F: \mathbf{C} \rightsquigarrow \mathbf{D}$ be a "functor", show that its "dual@@CAT" $\op{F}$ defined by $\op{A} \mapsto \op{(FA)}$ on "objects" and $\op{f} \mapsto \op{(Ff)}$ on "morphisms" is a "functor" $\op{\mathbf{C}} \rightsquigarrow \op{\mathbf{D}}$. 
\end{exer}
\begin{rem}\label{rem:hombifunctor}
	It is sometimes useful to "compose" the $\Hom$ "bifunctor@hombif" with other "functors" as follows. Given two "functors" $F,G: \mathbf{C} \rightsquigarrow \mathbf{D}$, there is a "functor" $\Hom_{\mathbf{D}}(F\placeholder,G\placeholder): \op{\mathbf{C}} \cattimes \mathbf{C} \rightsquigarrow \mathbf{D}$ acting on "objects" by $(X,Y) \mapsto \Hom_{\mathbf{D}}(FX,GY)$ and on "morphisms" by $(f,g) \mapsto Gg \circ (\placeholder) \circ Ff$.	One can check "functoriality" by showing
	\[\Hom_{\mathbf{D}}(F\placeholder,G\placeholder) = \Hom_{\mathbf{D}}(\placeholder,\placeholder) \circ (\op{F}\functimes G).\]
\end{rem}
%TODO: remark about opposite categories being simple to describe but their meaning is inscrutable because we really care about morphisms. For instance, Set^op is the category of complete atomic boolean algebras (it takes some time to prove this equivalence).
% The construction of the "opposite" "category"  looks rather simple, and the examples for "posets" and "groups" may give the impression that $\op{\mathbf{C}}$ is easy to understand. However, we but we would like to bring attention
\section{Duality in Action}
Let us start to illustrate how "duality@@CAT" can be useful while covering important definitions and results.
\begin{defn}[Monomorphism]
	\AP Let $\mathbf{C}$ be a "category", a "morphism" $f \in \mor{\mathbf{C}}$ is said to be ""monic"" (or a ""monomorphism"") if for any "parallel" "morphisms" $g$ and $h$ such that $(f,g), (f,h) \in \mathbf{C}_2$, $f\circ g = f\circ h$ implies $g = h$. Equivalently, $f$ is "monic" if $g = h$ whenever the following diagram "commutes".\footnote{According to Definition \ref{defn:commutative}, this diagram "commutes" if and only if $f \circ g = f \circ h$ because the "paths" $(f,g)$ and $(f,h)$ are the only "paths" of "length" bigger than one.}
	\begin{equation}\label{diag:defmonic}
		\begin{tikzcd}
		\bullet \arrow[r, "h"', bend right] \arrow[r, "g", bend left] & \bullet \arrow[r, "f"] & \bullet
		\end{tikzcd}
	\end{equation}
	Standard notation for a "monomorphism" is $ \bullet \hookrightarrow \bullet $ (\verb!\hookrightarrow!).
\end{defn}
\begin{prop}\label{prop:mon1}
	Let $\mathbf{C}$ be a "category" and $f:A\rightarrow B$ a "morphism", if there exists $f': B\rightarrow A$ such that $f'\circ f = \id_A$,\footnote{\AP We say that $f'$ is a ""left inverse"" of $f$.} then $f$ is a "monomorphism".
\end{prop}
\begin{proof}
	If $f\circ g = f\circ h$, then $f'\circ f \circ g = f'\circ f \circ h$ implying $g = h$.
\end{proof}
\AP Not all "monomorphisms" have a "left inverse", those that do are called ""split monomorphisms"".
\begin{prop}\label{prop:mon2}
	Let $\mathbf{C}$ be a "category" and $(f_1, f_2) \in \mathbf{C}_2$, if $f_1 \circ f_2$ is a "monomorphism", then $f_2$ is a "monomorphism".
\end{prop}
\begin{proof}
	Let $g,h \in \mor{\mathbf{C}}$ be such that $f_2\circ g = f_2\circ h$, we readily get that $(f_1\circ f_2)\circ g = (f_1 \circ f_2) \circ h$. Since $f_1\circ f_2$ is a "monomorphism", this implies $g = h$.
\end{proof}
The last two results hint at the fact that "monomorphisms" are analogues to injective functions and we will see that they are exactly the same in the "category" $\catSet$, but first let us introduce the "dual@@CAT" concept after the formal definition of "duality@@CAT". 
\begin{defn}[Duality]
	Given a definition or statement in an arbitrary "category" $\mathbf{C}$, one could view this concept inside the category $\op{\mathbf{C}}$ and obtain a similar definition or statement where all "morphisms" and the order of "composition" are reversed, this is called the ""dual@@CAT"" concept. Since $\op{\op{\mathbf{C}}} = \mathbf{C}$, taking the "dual@@CAT" is an involution, namely, the "dual@@CAT" of the "dual@@CAT" of a thing is that thing. For a definition or result where multiple \emph{arbitrary} "categories" are involved, the "dual" version is obtained by taking the "opposite" of all "categories".\footnote{Note the emphasis on the word ``arbitrary''. \AP For instance, a ""presheaf"" is a "functor" $F: \op{\mathbf{C}} \rightsquigarrow \catSet$ and the "dual@@CAT" concept is a ""copresheaf"", a "functor" $F: \mathbf{C} \rightsquigarrow \catSet$; we did not take the "opposite" of $\catSet$.} It is common but not systematic to refer to a "dual@@CAT" notion with the prefix ``co'' (e.g.: "presheaf" and "copresheaf").
	%TODO: check that this is true 
\end{defn}
"Dualizing@@CAT" the definition of a "monomorphism" yields an "epimorphism".
\begin{defn}[Epimorphism]
	Let $\mathbf{C}$ be a "category", a "morphism" $f \in \mor{\mathbf{C}}$ is said to be ""epic"" (or an ""epimorphism"") if for any two "parallel" "morphisms" $g$ and $h$ such that $(g,f), (h,f) \in \mathbf{C}_2$, $g\circ f = h\circ f$ implies $g = h$. Equivalently, $f$ is "epic" if $g = h$ whenever the following diagram commutes.\footnote{Seeing the diagrams make it clearer that the concepts are "dual@@CAT". Reversing the "arrows" in \eqref{diag:defmonic} yields \eqref{diag:defepic} and vice-versa.}
	\begin{equation}\label{diag:defepic}
	\begin{tikzcd}
	\bullet \arrow[r, "f"] & \bullet \arrow[r, "g", bend left] \arrow[r, "h"', bend right] & \bullet
	\end{tikzcd}
	\end{equation}
	Standard notation for an "epimorphism" is $ \bullet \twoheadrightarrow \bullet$ (\verb!\twoheadrightarrow!).
\end{defn}
The "dual@@CAT" versions of Propositions \ref{prop:mon1} and \ref{prop:mon2} also hold. Although translating our previous proofs to the "dual@@CAT" case is straightforward, we will do the two next proofs relying on "duality@@CAT" to convey the general sketch that works anytime a "dual@@CAT" result needs to be proven.
\begin{prop}\label{prop:ep1}
	Let $\mathbf{C}$ be a "category" and $f:A\rightarrow B$ a "morphism", if there exists $f': B\rightarrow A$ such that $f\circ f' = \id_B$, then $f$ is "epic".\footnote{\AP We say that $f'$ is a ""right inverse"" of $f$.}
\end{prop}
\begin{proof}
	Observe that $f$ is "epic" in $\mathbf{C}$ if and only if $\op{f}$ is "monic" in $\op{\mathbf{C}}$ (reverse the arrows in the definition).\footnote{This is another way to see that two concepts are "dual@@CAT".} Moreover, by definition, \[\op{f'} \circ \op{f} = \op{(f \circ f')} = \op{\id_B} = \id_{\op{B}},\] so by the result for "monomorphisms", $\op{f}$ is "monic" and hence $f$ is "epic". 
\end{proof}
\AP Not all "epimorphisms" have a "right inverse", those that do are called ""split epimorphisms"".
\begin{prop}
	Let $\mathbf{C}$ be a "category" and $(f_1, f_2) \in \mathbf{C}_2$, if $f_1 \circ f_2$ is "epic", then $f_1$ is "epic".
\end{prop}
\begin{proof}
	Since $\op{f_2} \circ \op{f_1} = \op{(f_1 \circ f_2)}$ is "monic", the result for "monomorphisms" implies $\op{f_1}$ is "monic" and hence $f_1$ is "epic".
\end{proof}
\begin{exmp}[$\catSet$]\label{exmp:monicset}
	We mentioned that "monomorphisms" are like generalizations of injective functions, and you may have guessed that "epimorphisms" are, in the same sense, generalizations of surjective functions. Let us make this precise.
	\begin{itemize}
		\item A function $f:A\rightarrow B$ is a "monomorphism" in $\catSet$ if and only if it is injective:\footnote{As a consequence, since all injective functions have a "left inverse", all the "monomorphisms" in $\catSet$ are "split@split monomorphism".}
		
		($\Leftarrow$) Since $f$ is injective, it has a "left inverse", so it is "monic" by Proposition \ref{prop:mon1}.
		
		($\Rightarrow$) Given $a \in A$, let $g_a: \{\ast\} \rightarrow A$ be the function sending $\ast$ to $a$. For any $a_1 \neq a_2 \in A$, the functions $g_{a_1}$ and $g_{a_2}$ are different, hence $f \circ g_{a_1} \neq f \circ g_{a_2}$. Therefore, $f(a_1) \neq f(a_2)$ implying $f$ is injective.
		
		\item A function $f:A\rightarrow B$ is an "epimorphism" if and only if it is surjective:\footnote{If you assume the axiom of choice, all surjective functions have a "right inverse" and thus all "epimorphisms" in $\catSet$ are "split@split epimorphism".}
		
		($\Leftarrow$) Since $f$ is surjective, it has a "right inverse", so it is "epic" by Proposition \ref{prop:ep1}.
		
		($\Rightarrow$) Let $h: B \rightarrow \{0,1\}$ be the constant function at $1$ and $g:B \rightarrow \{0,1\}$ be the indicator function of $\im(f) \subseteq B$, namely, \[g(x) = \begin{cases}1&\exists a \in A, x = f(a)\\0&\text{otherwise}\end{cases}.\]
		We see that $g \circ f = h\circ f$ are both constant at $1$, and $f$ being "epic" implies $g = h$. Thus, any element of $B$ is in the image of $f$, that is, $f$ is surjective.
	\end{itemize}
\end{exmp}

\begin{exmp}[$\catMon$]\label{exmp:monepiMON}
Inside the category $\catMon$, the "monomorphisms" are precisely the injective "homomorphisms@@MON".

($\Rightarrow$) Let $f:M\rightarrow M'$ be an injective "homomorphisms@@MON" and $g_1,g_2:N\rightarrow M$ be two "parallel" "homomorphisms@@MON". Suppose that $f\circ g_1 = f\circ g_2$, then for all $x \in N$, $f(g_1(x)) = f(g_2(x))$, so by injectivity of $f$, $g_1(x) = g_2(x)$. Therefore, $g_1 = g_2$ and since $g_1$ and $g_2$ were arbitrary, $f$ is a "monomorphism".

($\Leftarrow$) Let $f:M\rightarrow M'$ be a "monomorphism". Let $x,y \in M$ and define $p_x :(\N,+) \rightarrow M$ by $k\mapsto x^k$ and similarly for $p_y$. It is easy to show that $p_x$ and $p_y$ are "homomorphisms@@MON".\footnote{It follows from the definition of $x^k$ which is $x\stackrel{k}{\cdots}x$.} If $f(x) = f(y)$, then, by the "homomorphism@@MON" property, for all $k \in \N$
\[f(p_x(k))= f(x^k) = f(x)^k  = f(y)^k = f(y^k) = f(p_y(k)).\]
In other words, we get $f\circ p_x = f \circ p_y$, so $p_x = p_y$ and $x = y$. This direction follows.

Conversely, an "epimorphism" is not necessarily surjective. For example, the inclusion "homomorphism@@MON" $i:(\N,+) \rightarrow (\Z,+)$ is clearly not surjective, but it is an "epimorphism". Indeed, let $g,h: (\Z,+)\rightarrow M$ be two "monoid homomorphisms" satisfying $g \circ i = h\circ i$. In particular, $g(n) = h(n)$ for any $n \in \N\subset \Z$. It remains to show that also $g(-n) = h(-n)$: we have
\begin{gather*}
	h(n)g(-n) = g(n)g(-n) = g(n-n) = g(0) = 1_M\\
	h(-n)h(n) = h(-n+n) = h(0) = 1_M,
\end{gather*} but then $g(-n) = h(-n)h(n)g(-n) = h(-n)$.
\end{exmp}
\begin{exer}\label{exer:duality:monicCat}\marginnote{\hyperref[soln:duality:monicCat]{See solution.}}
	Show that a "monomorphism" in $\catCat$ is a "functor" that is "faithful" and injective on "objects", it is called an ""embedding@@CAT"".\footnote{Finding a nice characterization of "epimorphisms" in $\catCat$ is an open question as far as I know.} %TODO: check this.
\end{exer}
\begin{exer}\label{exer:duality:altdefmonepi}\marginnote{\hyperref[soln:duality:altdefmonepi]{See solution.}}
	Show that a "morphism" $f\in \mor{\mathbf{C}}$ is "monic" if and only if the function $\Hom_{\mathbf{C}}(A,f) = f \circ \placeholder$ is injective for all $A \in \obj{\mathbf{C}}$. "Dually@@CAT", show that $f$ is "epic" if and only if the function $\Hom_{\op{\mathbf{C}}}(\op{A},\op{f}) = \Hom_{\mathbf{C}}(f,A) = \placeholder \circ f$ is injective for all $A \in \obj{\mathbf{C}}$.
\end{exer}
\begin{rem}
	These alternative definitions of "monomorphisms" and "epimorphisms" are more categorical in nature. In fact, in the setting of \href{https://ncatlab.org/nlab/show/enriched+category+theory}{enriched category theory} they are preferable because they generalize easily.
\end{rem}
\begin{defn}[Isomorphism]\label{defn:isomorphism}
	\AP Let $\mathbf{C}$ be a "category", a "morphism" $f:A\rightarrow B$ is said to be an ""isomorphism@@CAT"" if there exists a "morphism" $f^{-1}: B\rightarrow A$ such that $f\circ f^{-1} = \id_B$ and $f^{-1}\circ f = \id_A$.\footnote{\AP Then $f^{-1}$ is called the ""inverse"" of $f$. One can check that if $f'$ is a "left inverse" of $f$ and $f''$ is a "right inverse", then $f' = f'' = f^{-1}$. Hence, the "inverse" is unique.}
\end{defn}
\begin{exer}\label{exer:duality:composemor}\marginnote{\hyperref[soln:duality:composemor]{See solution.}}
	Show that the property of being "monic"/"epic"/an "isomorphism@@CAT" is invariant under "composition", i.e., if $f$ and $g$ are "composable" "monomorphisms", then $f \circ g$ is "monic" and similarly for "epimorphisms" and "isomorphisms@@CAT".
\end{exer}
\begin{rem}
	The results shown about "monic" and "epic" "morphisms"\footnote{Proposition \ref{prop:mon1} and \ref{prop:ep1}.} imply that any "isomorphism@@CAT" is "monic" and "epic". However, the converse is not true as witnessed by the inclusion "morphism" $i$ described in Example \ref{exmp:monepiMON}.\footnote{This is not akin to the situation in $\catSet$ because, there, all "monomorphisms" and "epimorphisms" are "split" (assuming the axiom of choice).} \AP A "category" where all "monic" and "epic" "morphisms" are "isomorphisms@@CAT" (e.g.: $\catSet$) is called ""balanced"". \AP If there exists an "isomorphism@@CAT" between two objects $A$ and $B$, then they are ""isomorphic@@CAT"", denoted $A \isoCAT B$. \AP "Isomorphic@@CAT" objects are also "isomorphic@@CAT" in the "opposite" "category",\footnote{Because the "left inverse" becomes the "right inverse" and vice-versa.} that is, the concept of ""isomorphism@@CAT"" is ""self-dual"".
	
	For most intents and purposes, we will not distinguish between "isomorphic@@CAT" "objects" in a "category" because all the properties we care about will hold for one if and only if they hold for the other. This attitude should be somewhat familiar if you have done a bit of abstract algebra because it is natural to substitute the "group" $\Z/2\Z \times \Z/3\Z$ for $\Z/6\Z$ or $k^n$ for an $n$--dimensional "vector space" over $k$. It is less natural in $\catSet$ because, for instance, it equates the sets $\{0,1\}$ and $\{a,b\}$ which may be too coarse-grained for our intuition.
\end{rem} %TODO: continue this dicussion, isomorphisms are really important. Talk about evil stuff, and 

\begin{exmp}[$\catSet$]
	A function $f: X \rightarrow Y$ in $\mor{\catSet}$ has an "inverse" $f^{-1}$ if and only if $f$ is bijective, thus "isomorphisms@@CAT" in $\catSet$ are bijections. As a consequence, we have $A \isoCAT B$ if and only if $\cardinal{A} = \cardinal{B}$.\footnote{This is in fact the definition of cardinality.}
\end{exmp}
\begin{exmp}[$\catCat$]
	An "isomorphism@@CAT" in $\catCat$ is a "functor" $F:\mathbf{C} \rightsquigarrow \mathbf{D}$ with an "inverse" $F^{-1}: \mathbf{D} \rightsquigarrow \mathbf{C}$. This implies that $F_0$ and $F_1$ are bijections\footnote{\label{foot:bijfullfaith}When $F_0$ is a bijection, $F_1$ is a bijection if and only if $F$ is "fully faithful". Indeed, ...} because $(F^{-1})_0$ is the "inverse" of $F_0$ and $(F^{-1})_1$ is the "inverse" of $F_1$. %TODO: explain footnote

	Conversely, if $F:\mathbf{C} \rightsquigarrow \mathbf{D}$ is a "functor" whose component on "objects" and "morphisms" are bijective, we check that defining $F^{-1}: \mathbf{D} \rightsquigarrow \mathbf{C}$ with $(F^{-1})_0 := (F_0)^{-1}$ and $(F^{-1})_1 := (F_1)^{-1}$ yields a "functor".
	\begin{enumerate}[i.]
		\item Let $f\in \Hom_{\mathbf{D}}(A,B)$, by bijectivity of $F_0$ and $F_1$, there are $X,Y \in \obj{\mathbf{C}}$ and $g:X \rightarrow Y$ such that $FX = A$, $FY = B$ and $Fg = f$. Then, by definition,
		\begin{gather*}
			\source( F^{-1}f ) = \source(g) = X = F^{-1}FX = F^{-1} A\text{, and}\\
			\target( F^{-1}f ) = \target(g) = Y = F^{-1}FY = F^{-1} B.
		\end{gather*}
		\item For any $(f,f') \in \mathbf{D}_2$ with $f = Fg$ and $f' = Fg'$, we find \[F^{-1}(f \circ f') = F^{-1}(Fg \circ Fg') = F^{-1}F(g \circ g') = g \circ g' = F^{-1}Fg \circ F^{-1}Fg' = Ff \circ Ff'.\]
		\item For any $A \in \obj{\mathbf{D}}$ with $A = FX$, we find
		\[F^{-1}\id_A = F^{-1}\id_{FX} = F^{-1}F\id_X = \id_X = \id_{F^{-1}FX} = \id_{F^{-1}A}.\]
	\end{enumerate}
	We can conclude that "isomorphisms@@CAT" in $\catCat$ are precisely the "functors" which are bijective on "objects" and "morphisms". Furthermore, Footnote \ref{foot:bijfullfaith} implies they are precisely "fully faithful" "functors" that are bijective on "objects".
\end{exmp}
\begin{exmps}[Concrete categories]\label{exmps:isoconcrete}
	In a "concrete" "category" $\mathbf{C}$ with "forgetful" "functor" $U$, the underlying function of an "isomorphism@@CAT" $f$ must bijective because $U(f^{-1})$ is the inverse of $Uf$. This condition may be sufficient or not.
	\begin{enumerate}
		\item It is a simple exercise in an algebra class to show that "isomorphisms@@CAT" in the "categories" $\catMon$, $\catGrp$, $\catRing$, $\catField$ and $\catVect{k}$ are simply bijective "homomorphisms@@MON".\footnote{In fact, "isomorphisms@@CAT" are commonly defined as bijective "homomorphisms@@MON" in said algebra class.}
		\item\label{exmp:isoposet} In $\catPoset$, an "isomorphism@@CAT" between $(A,\leq_A)$ and $(B,\leq_B)$ is a bijective function $f: A \rightarrow B$ satisfying $a\leq_A a' \Leftrightarrow f(a) \leq_B f(a')$. Such a function is clearly "monotone", but its inverse is also "monotone" as for any $b\leq_B b'$, we have $ff^{-1}(b) \leq_B ff^{-1}(b') \implies f^{-1}(b) \leq_A f^{-1}(b')$.
		\itemAP In $\catTop$, it is not enough to have a bijective "continuous" function, we need to require that it has a "continuous" "inverse".\footnote{Consider $X = \{0,1\}$ with the two extreme "topologies" $\topo_{\codisc} = \{\emptyset,X\}$ and $\topo_{\disc} = \mP X$. The identity map $\id_X : (X, \topo_{\disc}) \rightarrow (X,\topo_{\codisc})$ is clearly bijective and "continuous", but its inverse is not "continuous". A similar example shows that a bijective "monotone" function is not necessarily a "poset" "isomorphism@@CAT".} Such functions are called ""homeomorphisms"".
	\end{enumerate}
\end{exmps}
\begin{defn}[Initial object]
	\AP Let $\mathbf{C}$ be a "category", an object $A \in \obj{\mathbf{C}}$ is said to be ""initial"" if for any $B \in \obj{\mathbf{C}}$, $\cardinal{\Hom_{\mathbf{C}}(A,B)} = 1$, namely there are no two "parallel" "morphisms" with "source" $A$ and every "object" has a "morphism" coming from $A$. The\footnote{We will soon see why we can use \textit{the} instead of \textit{an}.} "initial" "object" of a "category", if it exists, is denoted $\initial$ and the \textit{unique} "morphism" from $\initial$ to $X\in \obj{\mathbf{C}}$ is denoted $\initmorph: \initial \rightarrow X$.
\end{defn}
\begin{defn}[Terminal object]
	\AP Let $\mathbf{C}$ be a "category", an "object" $A \in \obj{\mathbf{C}}$ is said to be ""terminal""\footnote{The terminology "final" is also common.} if for any $B \in \obj{\mathbf{C}}$, $\cardinal{\Hom_{\mathbf{C}}(B,A)} = 1$, namely there are no two "parallel" "morphisms" with "target" $A$ and every "object" has a "morphism" going to $A$. The "terminal" "object" of a "category", if it exists, is denoted $\terminal$ and the \textit{unique} "morphism" from $X \in \obj{\mathbf{C}}$ into $\terminal$ is denoted $\termmorph:X \rightarrow \terminal$.
\end{defn}
\begin{rem}[Notation]
	The motivation behind the notations $\initial$ and $\terminal$ is given shortly, but the notations for the "morphisms" will be explained in Chapter \ref{chap:limits}.
\end{rem}
An "object" is "initial" in a "category" $\mathbf{C}$ if and only if it is "terminal" in $\op{\mathbf{C}}$, so these two concepts are "dual@@CAT". \AP Also, if an "object" is "initial" and "terminal", we say it is a ""zero"" "object" and usually denote it $\zero$.\footnote{Clearly, the concept of "zero" "object" is "self-dual".}
\begin{exmp}[$\catSet$]
	Let $X$ be a set, there is a unique function from the empty set into $X$, it is the empty function.\footnote{Recall (or learn here) that a function $f: A \rightarrow B$ is defined via subset of $f \subseteq A \times B$ that satisfies $\forall a \in A, \exists! b\in B, (a,b) \in f$. When $A$ is empty, $A \times B$ is empty and the only subset $\emptyset \subseteq A\times B$ satisfies the condition vacuously. In passing, when $B$ is empty but $A$ is not, the unique subset of $A \times B$ does not satisfy the condition, so there is no function $A \rightarrow \emptyset$.} We deduce that the empty set is the "initial" "object" in $\catSet$, hence the notation $\initial$. \AP For the "terminal" "object", we observe that there is a unique function $X \rightarrow \{\ast\}$ sending all elements of $X$ to $\ast$, thus $\intro*\termset = \{\ast\}$ is "terminal" in $\catSet$.
\end{exmp}
In this example, we could have chosen any singleton to show it is "terminal". However, that choice is irrelevant to a good category theorist because just as any two singletons are "isomorphic@@CAT" (because they have the same cardinality), any two "terminal" "objects" are "isomorphic@@CAT".
\begin{prop}\label{prop:initialunique}
	Let $\mathbf{C}$ be a "category" and $A,B\in \obj{\mathbf{C}}$ be "initial", then $A \isoCAT B$.
\end{prop}
\begin{proof}
	Let $f$ be the single element in $\Hom_{\mathbf{C}}(A,B)$ and $f'$ be the single element in $\Hom_{\mathbf{C}}(B,A)$. Both the "identity" "morphism" $\id_A$ and $f' \circ f$ belong to $\Hom_{\mathbf{C}}(A,A)$ which must have cardinality $1$ because $A$ is "initial". Similarly $\id_B$ and $f \circ f'$ belong to $\Hom_{\mathbf{C}}(B,B)$ which has cardinalty $1$ because $B$ is "initial". We conclude that $f' \circ f = \id_A$ and $f\circ f' = \id_B$. In words, $f$ and $f'$ are "inverses", thus $A \isoCAT B$. 
\end{proof}
\begin{cor}["Dual@@CAT"]\label{cor:terminalunique}
	Let $\mathbf{C}$ be a "category" and $A,B\in \obj{\mathbf{C}}$ be "terminal", then $A \isoCAT B$.\footnote{From now on, I let you prove many "dual@@CAT" results on your own --- I will try to continue doing the complicated ones. They are not necessarily great exercises, but you can certainly do them if you want to follow this book at a slower pace.}
\end{cor}
Rewording the last two results, we can say that "initial" (resp. "terminal") "objects" are unique up to "isomorphisms@@CAT". However, the situation is quite nicer. "Initial" (resp. "terminal") "objects" are unique up to  \textit{unique} "isomorphisms@@CAT". Indeed, if there is an "isomorphism@@CAT" $f: A \rightarrow B$ and $A$ and $B$ are "initial" (resp. "terminal"), then, by definition, $f$ is the unique "morphism" in $\Hom_{\mathbf{C}}(A,B)$. %TODO: Note that the uniqueness of isomorphism is stronger than a simple isomorphism (try to give more intuition about this with an example)
\begin{exer}\label{exer:duality:inittermcat}\marginnote{\hyperref[soln:duality:inittermcat]{See solution.}}
	Show that in $\catCat$, the "initial" "object" is the empty "category" (no "objects" and no "morphisms") and the "terminal" "object" is the "category" with one "object" $\termcat$ (hence the agreeing notation).\footnote{\textbf{Hint}: the unique functor $\termmorph:\mathbf{C} \rightarrow \termcat$ is the "constant functor" at the "object" $\bullet \in \obj{\termcat}$.}
\end{exer}
\begin{exmp}[$\catGrp$]
	Similarly to $\catSet$, the "trivial group" with one element is "terminal" in $\catGrp$. Moreover, note that there are no empty "group" (because a "group" must contain an "identity@@GRP" element), but any "group homomorphism" from the "trivial group" $\{1\}$ into a "group" $G$ must send $1$ to $1_G$, which completely determines the "homomorphism@@GRP". Therefore, the "trivial group" is also "initial" in $\catGrp$, it is the "zero" "object".
\end{exmp}
\begin{exmp}[$\catMet$]\label{exmp:terminitmet}
	The "terminal" "object" in $\catMet$ is the space with only one point $\ast$. The distance is determined by the axioms on a "metric", because $d_{\terminal}(\ast,\ast)$ must be equal to $0$.\footnote{The function sending all of $X$ to $\ast$ is nonexpansive whatever the distance $d$ on $X$ because $d(x,y) \geq 0 = d_{\terminal}(\ast,\ast)$.} The "initial" "object" in $\catMet$ is the empty space, for the same reason that $\emptyset$ is "initial" in $\catSet$.
\end{exmp}
\begin{exer}\label{exer:duality:zeroinptd}\marginnote{\hyperref[soln:duality:zeroinvect]{See solution.}}
	Find the "initial" and "terminal" "objects" in $\catPtd$.
\end{exer}
\begin{exer}\label{exer:duality:zeroinvect}\marginnote{\hyperref[soln:duality:zeroinvect]{See solution.}}
	Find the "initial" and "terminal" "objects" in $\catVect{k}$.
\end{exer}
\begin{exer}\label{exer:duality:terminalinitial}\marginnote{\hyperref[soln:duality:terminalinitial]{See solution.}}
	Find a "category" with only two "objects" $X$ and $Y$ such that
	\begin{enumerate}[(a)]
		\item $X$ is "initial" but not "terminal" and $Y$ is "terminal" but not "initial".
		\item $X$ is "initial" but not "terminal" and $Y$ neither "terminal" nor "initial".
		\item $X$ is "terminal" but not "initial" and $Y$ is neither "terminal" nor "initial".
		\item $X$ is "initial" and "terminal" and $Y$ is neither "terminal" nor "initial".
	\end{enumerate} 
\end{exer}
\begin{exmps}
	Here are more examples of "categories" where "initial" and "terminal" "objects" may or may not exist.
	\begin{enumerate}
		\begin{marginfigure}[3\baselineskip]
			\begin{equation}\label{diag:Ngeq}
				\begin{tikzcd}
				\stackrel{0}{\bullet}  & \arrow[l] \stackrel{1}{\bullet}  & \arrow[l] \stackrel{2}{\bullet}  & \arrow[l] \cdots
				\end{tikzcd}
			\end{equation}
		\end{marginfigure}
		\item $\exists$ "terminal", $\nexists$ "initial": Consider the "poset" $(\N, \geq)$ represented by diagram \eqref{diag:Ngeq}. It is clear that $0$ is "terminal" and no element can be "initial" because $0 \geq x$ implies $x = 0$.
		
		\item %TODO: change this for the field with characteristic p or 0.
		$\nexists$ "terminal", $\exists$ "initial":\footnote{Of course, you could take the opposite of $(\N, \geq)$, that is $(\N, \leq)$, but that is not fun.} Recall the "category" $\mathbf{SetInj}$ of finite sets and injective functions. The empty set is still "initial" but the singletons are not "terminal" because a function from a set $S$ into $\{\ast\}$ is never injective when $\cardinal{S} > 1$.
		% The "category" \textbf{FinGrpInj} where the "objects" are finite "groups" and the "morphisms" are injective "homomorphisms@@GRP" only contains an "initial" "object" $\{1\}$. Indeed, an injective "homomorphism@@GRP" $G \hookrightarrow H$ can be seen as "subgroup" of $H$ "isomorphic@@GRP" to $G$. The "trivial" "group" $\{1\}$ can only be "isomorphic@@GRP" to the "subgroup" $\{1_H\}$ as any other element has degree more than $1$, so $\{1\}$ is "initial". Moreover, a "group" $G$ cannot be "terminal" as $G \times (\Z/2\Z)$ cannot be "isomorphic@@GRP" to any "subgroup" of $G$.
		\item $\nexists$ "terminal", $\nexists$ "initial": Let $G$ be a non-"trivial group", the "delooping" of $G$ has no "terminal" and no "initial" "objects". The "category" $\deloop{G}$ has a single "object" $\deloopobject$ with $\Hom_{\deloop{G}}(\deloopobject, \deloopobject) = G$, so $\deloopobject$ cannot be "initial" nor "terminal" when $\cardinal{G} > 1$.
		
		For a more interesting example, consider the "category" $\catField$. Its underlying "directed graph" is disconnected\footnote{There are "objects" with no "morphisms" between them.} because there are no "field homomorphisms" between "fields" of different "characteristic". Therefore, $\catField$ has no "initial" nor "terminal" "objects".
		\item $\exists$ "terminal", $\exists$ "initial": The empty set is both "initial" and "terminal" in the "category" $\catRel$ because a relation $\emptyset \rightarrow A$ (resp. $A \rightarrow \emptyset$) is a subset of $\emptyset \times A$ (resp. $A \times \emptyset$), and the latter has a unique subset for all sets $A$.
		
		For an example with no "zero" "object", let $X$ be a non-empty "topological space" where $\tau$ is the collection of "open sets".\footnote{Recall that it must contain $\emptyset$ and $X$.} The "category" of "open sets" $\catOpens(X)$ satisfies
		\[\Hom_{\catOpens(X)}(U,V) = \begin{cases}\{i_{U,V}\} & U \subseteq V\\ \emptyset & U \not\subseteq V\end{cases}\]
		Since the empty set is contained in every "open set", it is an "initial" "object". Since the full set $X$ contains every "open set", it is a "terminal" "object". Any other set cannot be "initial" as it cannot be contained in $\emptyset$ nor "terminal" as it cannot contain $X$. Moreover, note that the two objects are not "isomorphic@@CAT" because $X \not\subseteq \emptyset$.
	\end{enumerate}
\end{exmps}

\begin{exer}\label{exer:duality:morterminal}\marginnote{\hyperref[soln:duality:morterminal]{See solution.}}
	Let $\mathbf{C}$ be a "category" with a "terminal" "object" $\terminal$. Show that any "morphism" $f: \terminal \rightarrow X$ is "monic". State and prove the "dual@@CAT" statement.
\end{exer}
\begin{exer}\label{exer:duality:productterminal}\marginnote{\hyperref[soln:duality:productterminal]{See solution.}}
	Let $\mathbf{C}$ and $\mathbf{D}$ be "categories", and $\terminal_{\mathbf{C}}$ and $\terminal_{\mathbf{D}}$ be "terminal" "objects" in $\mathbf{C}$ and $\mathbf{D}$ respectively. Show that $(\terminal_{\mathbf{C}},\terminal_{\mathbf{D}})$ is "terminal" in the $\mathbf{C} \cattimes \mathbf{D}$. State and prove the "dual@@CAT" statement.
\end{exer}
\begin{exmp}\label{exmp:unions}
For our last application of "duality@@CAT" in this section,\footnote{Do not worry, we will have plenty of opportunities to use "duality@@CAT" later.} let $X$ be a set and consider the "posetal" "category" $(\mP X, \subseteq)$. We would like to define the union of two subsets of $X$ in this "category". The usual definition $A \cup B = \{x \in X \mid x \in A \text{ or } x \in B\}$ is not suitable because the data in the "posetal" "category" $\mP X$ never refers to elements of $X$. In particular, the subsets $A,B \subseteq X$ are simply "objects" in the "category" and it is not clear to us how we can determine what elements are in $A$ and $B$ with our categorical tools ("objects" and "morphisms").

We propose another characterization of the union of $A$ and $B$. First, what is obvious, $A \cup B$ contains $A$ and it contains $B$. Second, $A \cup B$ is the smallest subset of $X$ containing $A$ and $B$. Indeed, if $Y \subseteq X$ contains all elements in $A$ and $B$, then it also contains $A \cup B$. Using the order $\subseteq$ (or equivalently, the "morphisms" in the "category" $\mP X$), we have\footnote{We leave it as an exercise to show that $A \cup B$ is the only subset of $X$ satisfying this property.} \[A, B \subseteq A\cup B \text{ and }\forall Y \text{ s.t. } A, B \subseteq Y \text{ then } A\cup B \subseteq Y.\] This yields a definition of $\cup$ within the "category" $\mP X$, which means we can look in the "opposite" of $\mP X$ and "dualize@@CAT" $\cup$.

The "dual@@CAT" of this property (reversing all inclusions) is as follows.\footnote{The symbol $\square$ is a placeholder for the operation which we will find to be "dual@@CAT" to union.}
\[ A \square B \subseteq A, B \text{ and } \forall Y \text{ s.t. } Y \subseteq A,B \text{ then } Y \subseteq A \square B\]
Putting this in words, $A \square B$ is the largest subset of $X$ which is contained in $A$ and $B$. That is, of course, the intersection $A \cap B$. In this sense, union and intersection are "dual@@CAT" operations. If you search your memory for properties about union and intersection that you proved when you first learned about sets, you will find that they usually come in pairs, the first property being the "dual@@CAT" of the second.\footnote{e.g.: \[A \cap (B \cup C) = (A \cap B) \cup (A \cap C)\]\[A \cup (B \cap C) = (A \cup B) \cap (A \cup C)\]}
\end{exmp}

\section{More Vocabulary}
In the next chapter, we will start heavily using diagrams, and in order to generalize many concepts relying on diagrams, we will need a formal abstract definition of diagrams to work with. We introduce this definition here\footnote{In the rest of the book, we use the term \textit{diagram} to refer to both the informal pictures we draw and the formal mathematical object defined below. The context should disambiguate the two usages, but if you are not sure, rememeber that only the latter use will appear with a hyperlink on the word that links to Definition \ref{defn:diagram}.} and throw in a couple of new concepts and their "duals@@CAT" to keep practicing with the central idea in this chapter.
\begin{defn}[Diagram]\label{defn:diagram}
    \AP A ""diagram"" in $\mathbf{C}$ is a "functor" $F:\mathbf{J}\rightsquigarrow \mathbf{C}$ where $\mathbf{J}$ is usually a "small" or even finite "category". \AP We say that $J$ is the ""shape"" of the "diagram" $F$.
\end{defn}
\begin{rem}
\begin{marginfigure}[5\baselineskip]
    \begin{equation}\label{diag:commsquare}
        \begin{tikzcd}
            \cdot \arrow[r] \arrow[d] & \cdot \arrow[d] \\
            \cdot \arrow[r] & \cdot
        \end{tikzcd}
    \end{equation}
\end{marginfigure}
"Diagrams" are usually represented by (partially) drawing the image of $F$. While all the informal diagrams drawn up to this point can correspond to actual formal "diagrams", it is not very pertinent to highlight this correspondence in a case-by-case basis. Indeed, the motivation behind Definition \ref{defn:diagram} is the need to abstract away from the drawings to work in more generality. For instance, when considering a "commutative" square in $\mathbf{C}$, it can be helpful to view it as the image of a "functor" with codomain $\mathbf{C}$ and domain the "category" $\mathbf{2}\product \mathbf{2}$ represented in \eqref{diag:commsquare}.
\end{rem}
Since "diagrams" are defined as "functors", they interact well with other "functors". For example, if $F: \mathbf{J} \rightsquigarrow \mathbf{C}$ is a "diagram" of "shape" $\mathbf{J}$ in $\mathbf{C}$ and $G: \mathbf{C}\rightsquigarrow \mathbf{D}$ is a "functor", then $G\circ F$ is a "diagram" of "shape" $\mathbf{J}$ in $\mathbf{D}$. Some "functors" interact even more nicely with "diagrams".
\begin{defn}\label{defn:presreflprop}
	Let $F: \mathbf{C} \rightsquigarrow \mathbf{C}'$ be a "functor" and $P$ a property\footnote{This is intentionally a vague term. In Chapter \ref{chap:limits}, we will have a more formal but less general definition of "preserving@@PROP" and "reflecting@@PROP".} of "diagrams".
	\begin{itemize}
		\itemAP[-] We say that $F$ ""preserves@@PROP"" "diagrams" with property $P$ if for any "diagram" $D: \mathbf{J} \rightsquigarrow \mathbf{C}$, if $D$ has property $P$, then $F \circ D$ has property $P$.
		\itemAP[-] We say that $F$ ""reflects@@PROP"" "diagrams" with property $P$ if for any "diagram" $D: \mathbf{J} \rightsquigarrow \mathbf{C}$, if $F \circ D$ has property $P$, then $D$ has property $P$.
	\end{itemize}
\end{defn}
\begin{warn}
	"Preserving@@PROP" and "reflecting@@PROP" a property $P$ are not "dual@@CAT" notions. The "dual@@CAT" of "preserving" (resp. "reflecting@@PROP") $P$ is "preserving" (resp. "reflecting@@PROP") the "dual@@CAT" of $P$. 
\end{warn}
\begin{exmp}["Commutativity"]
	By drawing the "objects" and "morphisms" in the image of a "diagram" $D: \mathbf{J} \rightsquigarrow \mathbf{C}$, we can still use Definition \ref{defn:commutative} to say whether $D$ is "commutative" or not. Since "functors" preserve "composition", if $D$ is "commutative" and $F: \mathbf{C} \rightsquigarrow \mathbf{D}$ is any "functor", $F\circ D$ is also "commutative". Indeed, if two "paths" in $\mathbf{C}$ "compose@comppaths" to the same "morphism", then the "composites@comppaths" of the "paths" after applying $F$ are still equal. In other words, all "functors" "preserve@@PROP" "commutativity". We will use this fact many times in proofs\footnote{Without the rigor of defining the "functor" represented by the diagrams.} by drawing a "commutative" diagram and applying $F$ to all "objects" and "morphisms" to get another "commutative" diagram.

	"Commutativity" is not "reflected@@PROP" by all "functors". Even if a "diagram" $D: \mathbf{J} \rightsquigarrow \mathbf{C}$ does not "commute", "composing" $D$ with the unique "functor" into the "terminal" "category" $\termcat$ yields a (trivially) "commutative" "diagram" $\termmorph \circ D : \mathbf{J} \rightsquigarrow \termcat$.

	If $F: \mathbf{C} \rightsquigarrow \mathbf{D}$ is "faithful", then $F$ "reflects@@PROP" "commutativity". Let $D: \mathbf{J} \rightsquigarrow \mathbf{C}$ be a "diagram" and suppose $F \circ D$ is "commutative". As in Definition \ref{defn:commutative}, take a "path" in the image of $D$ of "length" greater than one that "composes@comppaths" to $p_1: A \rightarrow B$ and another "path" that "composes@comppaths" to $p_2 : A \rightarrow B$. After applying $F$, "commutativity" of $F\circ D$ ensures the two "paths" "compose@comppaths" to the same "morphism" $p \in \Hom_{\mathbf{D}}(FA, FB)$. Moreover, $p$ is the image of both $p_1$ and $p_2$, and since $F$ is "faithful", we conclude that $p_1 = p_2$.
\end{exmp}
The following two exercises are a quick investigation in "preservation@@PROP" and "reflection@@PROP" of simple properties we have seen in this chapter.
\begin{exer}\label{exer:duality:preserving}\marginnote{\hyperref[soln:duality:preserving]{See solution.}}
	\begin{enumerate}
        \item Find an example of "functor" which does not "preserve@@PROP" "monomorphisms".\footnote{We can see a "morphism" as a "diagram" of "shape" $\cattwo$ because a "functor" $\cattwo \rightsquigarrow \mathbf{C}$ amounts to a choice of a "morphism" in $\mathbf{C}$. Thus, a "functor" $F$ "preserves@@PROP" "monomorphisms" if and only if whenever $f$ is "monic", $F(f)$ also is.}
        \item Show that if $f \in \mathbf{C}_1$ is a "split monomorphism", then $F(f)$ is also a "split monomorphism", i.e.: any "functor" "preserves@@PROP" "split monomorphisms".
        \item State and prove the "dual@@CAT" statement.
        \item Infer that all "functors" "preserve@@PROP" "isomorphisms@@CAT", in particular "functors" send "isomorphic@@CAT" "objects" to "isomorphic@@CAT" "objects".
    \end{enumerate}
\end{exer}
\begin{exer}\label{exer:duality:reflecting}\marginnote{\hyperref[soln:duality:reflecting]{See solution.}}
	\begin{enumerate}
		\item Find an example of "functor" which does not "reflect@@PROP" "monomorphisms".\footnote{A "functor" "reflects" "monomorphisms" if whenever $Ff$ is "monic", $f$ also is.}
		\item Show that if $F$ is "faithful", then $F$ "reflects@@PROP" "monomorphisms".
		\item State and prove the "dual@@CAT" statement.
	\end{enumerate}
\end{exer}
%TODO: exercise about functors preserving and reflecting initial and terminal objects.
%sub object, quotient object.
%
% \item We say that a functor $F: \mathbf{C} \rightsquigarrow \mathbf{D}$ \textbf{preserves} monomorphisms if whenever $f \in \mathbf{C}_1$ is monic, then $F(f)$ is also monic.
%     \begin{enumerate}
%         \item Find an example of functor which does not preserve monomorphisms.
%         \item Show that if $f \in \mathbf{C}_1$ is a split monomorphism, then $F(f)$ is also a split monomorphism, i.e.: any functor preserves split monomorphisms.
%     \end{enumerate}
%     State the dual definition and the dual statements and prove them. Infer that all functors preserve isomorphisms, in particular functors send isomorphic objects to isomorphic objects.
%     \item We say that a functor $F: \mathbf{C} \rightsquigarrow \mathbf{D}$ \textbf{reflects} monomorphisms if whenever $F(f) \in \mathbf{D}_1$ is monic, then $f$ is monic.
%     \begin{enumerate}
%         \item Find an example of functor which does not reflect monomorphisms.
%         \item Show that if $F$ is faithful, then $F$ reflects monomorphisms.
%     \end{enumerate}
%     State the dual definition and the dual statements and prove them.
%     \item Let $X \in \mathbf{C}_0$ be an object, the set \textbf{subobjects} of $X$, denoted $\text{Sub}_{\mathbf{C}}(X)$, is the set of monomorphisms into $X$ quotiented by 
%     Denoting $[m]$ the equivalence class of $m$, $\text{Sub}_{\mathbf{C}}(X)$ has a poset structure defined by \[m \leq m' \Leftrightarrow \exists \text{ morphism } k, m = m'k.\]
%     Show that $\sim$ is an equivalence relation and $\leq$ is a partial order on $\text{Sub}_{\mathbf{C}}(X)$.
We have seen how to \textit{categorify}\footnote{Categorification is an imprecise term referring to the process of casting an idea in a more categorical language. Depending on the original idea and the context where it is used, there can be many ways to describe it with a categorical mind. In the following two chapters, we will spend some time categorifying several set-theoretical notions.} unions and intersections of subsets in Example \ref{exmp:unions}. The next set theoretical notion we categorify is subsets. A subset $I \subseteq S$ can be identified with the inclusion function $I \hookrightarrow S$, and since the latter is injective, we may want to consider "monomorphisms" with "target" $S$ to be some kind of generalized subset. Observe however that an injection $I \hookrightarrow S$ is not necessarily an inclusion function. This does not matter because, in reality, we are interested in the image of this injection. We run into another obstacle because if two injections into $S$ have the same image, they represent the same subset. We overcome this using the following exercise.
\begin{exer}\label{exer:duality:equivsubobj}\marginnote{\hyperref[soln:duality:equivsubobj]{See solution.}}
	\begin{marginfigure}[1\baselineskip]
		Two "monomorphisms" related by $\sim$.
		\begin{equation*}
			% https://q.uiver.app/?q=WzAsMyxbMCwwLCJcXGJ1bGxldCJdLFsxLDEsIlxcYnVsbGV0Il0sWzIsMCwiXFxidWxsZXQiXSxbMCwxLCJtIiwyLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoiaG9vayIsInNpZGUiOiJ0b3AifX19XSxbMiwxLCJtJyIsMCx7InN0eWxlIjp7InRhaWwiOnsibmFtZSI6Imhvb2siLCJzaWRlIjoidG9wIn19fV0sWzAsMiwiaSJdXQ==
			\begin{tikzcd}
				\bullet && \bullet \\
				& \bullet
				\arrow["m"', hook, from=1-1, to=2-2]
				\arrow["{m'}", hook, from=1-3, to=2-2]
				\arrow["i", from=1-1, to=1-3]
			\end{tikzcd}
		\end{equation*}
	\end{marginfigure}
	Let $\mathbf{C}$ be a "category" and $X \in \obj{\mathbf{C}}$, we define the relation $\sim$ on "monomorphisms" with "target" $X$ by \[m \sim m' \Leftrightarrow \exists \text{ "isomorphism@@CAT" } i,  m = m' \circ i.\]
	Show that $\sim$ is an equivalence relation.
\end{exer}
\begin{defn}[Subobject]
	\AP Let $\mathbf{C}$ be a "category", a ""subobject"" of $X \in \obj{\mathbf{C}}$ is an equivalence class of the relation $\sim$ defined above. We will often abusively refer to a "subobject" simply with a "monomorphism" $Y \hookrightarrow X$ representing the class. The "collection" of "subobjects" of $X$ is denoted $\Sub_{\mathbf{C}}(X)$. \AP If for any $X \in \obj{\mathbf{C}}$, $\Sub_{\mathbf{C}}(X)$ is a set, we say that $\mathbf{C}$ is ""well-powered"".
\end{defn}
\begin{exmp}[$\catSet$]\label{exmp:subobjsubset}
	Let $X \in \obj{\catSet}$, "subobjects" of $X$ correspond to subsets of $X$.\footnote{The notation $\Sub_{\catSet}(X)$ is perfect!} Indeed, any subset $I \subseteq X$ has an inclusion function $i: I \hookrightarrow X$ which is injective, hence "monic". For the other direction, we can show that $i:I \hookrightarrow X$ and $j: J \hookrightarrow X$ are in the same equivalence class in $\Sub_{\catSet}(X)$ if and only if $\im(i) = \im(j)$.\footnote{($\Rightarrow$) If $i \sim j$, then there exists a bijection $f$ such that $i = j \circ f$. It follows that the image of $j$ is the image of $i$.
	
	($\Leftarrow$) Suppose $\im(i)=\im(j)$, we define $f:I \rightarrow J = x \mapsto j^{-1}(i(x))$, where $j^{-1}$ is the "left inverse" of $j$. It is clear that $i = j \circ f$ and a quick computation shows $f$ is an "isomorphism@@CAT" with "inverse" $x\mapsto i^{-1}(j(x))$, where $i^{-1}(x)$ is the "left inverse" of $i$.} We conclude that the correspondence between $\Sub_{\catSet}(X)$ and $\mPcov(X)$ sends $[i]$ to the image of $i$ and $I\subseteq X$ to the equivalence class of the inclusion $i: I \hookrightarrow X$.
\end{exmp}
The next exercise generalizes the "poset" of subsets of $X$ $(\mP X, \subseteq)$.
\begin{exer}\label{exer:duality:posetsubobj}\marginnote[\baselineskip]{\hyperref[soln:duality:posetsubobj]{See solution.}}
	Let $\mathbf{C}$ be a "category" and $X \in \obj{\mathbf{C}}$, we define the relation $\leq$ on $\Sub_{\mathbf{C}}(X)$: 
	\[[m] \leq [m'] \Leftrightarrow \exists \text{ "morphism" } k,  m = m' \circ k.\]
	Show that $\leq$ is a well-defined "partial order".
\end{exer}
\begin{exer}\label{exer:duality:posetsubset}\marginnote{\hyperref[soln:duality:posetsubset]{See solution.}}
	Show that the correspondence between $\mP X$ and $\Sub_{\catSet}(X)$ from Example \ref{exmp:subobjsubset} is an "isomorphism@@CAT" of "posets" $(\mP X, \subseteq) \cong (\Sub_{\catSet}(X), \leq)$.\footnote{We saw what "poset" "isomorphisms@@CAT" were in Example \ref{exmps:isoconcrete}.\ref{exmp:isoposet}.}
\end{exer}
\begin{exer}\label{exer:duality:subobjccat}\marginnote{\hyperref[soln:duality:subobjccat]{See solution.}}
	Show that a "subobject" in $\catCat$ is a "subcategory".
\end{exer}
We can use "duality@@CAT" to obtain (for free) the notion of "quotient objects".
\begin{defn}[Quotients]
	Let $\mathbf{C}$ be a "category" and $X \in \obj{\mathbf{C}}$, there is an equivalence relation $\sim$ on "epimorphisms" with "source" $X$ defined by \[q \sim q' \Leftrightarrow \exists \text{ "isomorphism@@CAT" } i,  q = i \circ q'.\]
	\AP A ""quotient object"" (or simply "quotient@@CAT") of $X$ is an equivalence class of the relation $\sim$ defined above.\footnote{We will often abusively refer to a "quotient@@CAT" simply with an "epimorphism" $X \twoheadrightarrow Y$.} The "collection" of "quotients@@CAT" of $X$ is denoted $\Quot_{\mathbf{C}}(X)$. \AP If for any $X \in \obj{\mathbf{C}}$, $\Quot_{\mathbf{C}}(X)$ is a set, we say that $\mathbf{C}$ is ""co-well-powered"". There is a "partial order" $\leq$ on $\Quot_{\mathbf{C}}(X)$ defined by 
	\[[q] \leq [q'] \Leftrightarrow \exists \text{ "morphism" } k,  q = k \circ q'.\]
\end{defn}
The terminology for this "dual@@CAT" notion is motivated by the following exercise.
\begin{exer}\label{exer:duality:quotientgrp}\marginnote{\hyperref[soln:duality:quotientgrp]{See solution.}}
	Show that a "quotient object" of $G \in \obj{\catGrp}$ is a "quotient group" of $G$.
\end{exer}
%TODO: example in groups. (need to state first isomorphism theorem)
%TODO: add other stuff when needed later.

I love finding a categorical definition for something I am used to thikning of in classical terms.\footnote{This feeling led me to study more category theory.} It facilitates a better understanding of the essential components of the classical notion, and "duality@@CAT" can open the gates to a parallel world where we can have just as much fun.

For now, we only played with definitions without discovering anything deep. Some people maintain it is useless to take a categorical point of view if it does not lead to new results. Category theorists (I presume) believe that it helps organize our thoughts regardless of the mathematical outcomes. The rest of the book focuses on practicing categorical thinking without necessarily demonstrating its advantages other than its unifying/orgasitional power.

\end{document}